### 2025-06-13 conteudo/methods/methods.tex
add me

For the first ArKanjo-related alternative, a teaching assistant ran the tool on the IIO subsystem, 
creating a list of duplicated function pairs found with a 90\% similarity threshold. The students' 
task was to refactor the code to mitigate these specific duplications and then navigate the process 
of submitting their patches to the IIO maintainers for review.

>>>>

For the first ArKanjo-related alternative, a teaching assistant ran the tool on the IIO subsystem, 
creating a list of duplicated function pairs found with a 90\% similarity threshold. The students' 
task was to refactor the code to mitigate these specific duplications and then pass through the process 
of submitting their patches to the IIO maintainers for review.
